### 2021-03-04 article/paper_eng.tex
acknowledgments
title page, 10pt font

% \listfiles
\documentclass[a4paper]{article}
\usepackage[T2A]{fontenc}
% \usepackage[english, russian]{babel}
\usepackage{sectsty}
\sectionfont{\centering\normalfont}
\subsectionfont{\centering\normalfont}
\subsubsectionfont{\normalfont}
\usepackage{changepage}
\usepackage{filecontents}
% \usepackage{mathptmx}
\usepackage{float} 
\usepackage{subcaption}
\usepackage[utf8]{inputenc}
\usepackage[14pt]{extsizes}
\usepackage{physics} 
\usepackage{graphicx}
\usepackage{enumerate}
\graphicspath{{../misc/}}
\usepackage{setspace,amsmath}
% \usepackage[left=30mm, right=15mm, top=20mm, bottom=20mm]{geometry} 
\usepackage[nottoc]{tocbibind}
\usepackage[style=gost-numeric,sorting=none,backend=biber,defernumbers=false]{biblatex}
\DeclareBibliographyAlias{misc}{article}
\addbibresource{lit.bib} 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \everymath{\displaystyle}
\DeclareMathSizes{12}{20}{14}{10}

@@

\begin{center}
    \large\textbf{Training inhibitory connections between local receptive fields in spiking neural networks}\\
    \hfill\break

    Daniil Gafni, Dmitry Nekhaev, Vyacheslav Demin
\end{center}

% \tableofcontents

% \pagebreak

\addcontentsline{toc}{section}{Abstract}
\section*{Abstract}
Standard learning methods (based on the error backpropagation) used in formal artificial neural networks (ANNs) are difficult to apply to spiking neural networks (SNNs) due to discrete and time-distributed nature of the events they generate --- impulses, or spikes. Although such projects exist, local learning algorithms, which are more biologically correct, capable of performing unsupervised learning (without a teacher) and more energy efficient (if implemented on specialized hardware), are of greater interest.

One of the main disadvantages of the SNNs in comparison with the ANNs is the current understudy of local learning rules, and because of this, lower quality metrics (on inference) of algorithms based on SNNs. Thus, the study of SNN learning algorithms, like spike-timing-dependent-plasticity (STDP), for use in various SNN architectures is an important task.

The introduction of inhibitory connections (having negative weights) allows to achieve a better distinction of features learned by the neurons. In this work, it is shown that learning competition relationships in the architecture of a locally connected SNN potentially allows to achieve better results in the accuracy of pattern recognition (on MNIST digits) due to the organization of competition and cooperation between groups of neurons.

@@

\begin{center}
All the study materials and the code implementation can be found at\\
\href{https://github.com/danielgafni/bachelor}{https://github.com/danielgafni/bachelor} 
\end{center}

>>>>

% \listfiles
\documentclass[a4paper,10pt]{article}
\usepackage[T2A]{fontenc}
% \usepackage[english, russian]{babel}
\usepackage{sectsty}
\sectionfont{\centering\normalfont}
\subsectionfont{\centering\normalfont}
\subsubsectionfont{\normalfont}
\usepackage{changepage}
\usepackage{filecontents}
\usepackage{array}
\usepackage{float} 
\usepackage{subcaption}
\usepackage[utf8]{inputenc}
\usepackage[14pt]{extsizes}
\usepackage{physics} 
\usepackage{graphicx}
\usepackage{enumerate}
\graphicspath{{../misc/}}
\usepackage{setspace,amsmath}
\usepackage{bigstrut}
\usepackage{tabularx}
% \usepackage[left=30mm, right=15mm, top=20mm, bottom=20mm]{geometry} 
\usepackage[nottoc]{tocbibind}
\usepackage[style=gost-numeric,sorting=none,backend=biber,defernumbers=false]{biblatex}
\DeclareBibliographyAlias{misc}{article}
\addbibresource{lit.bib} 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \everymath{\displaystyle}
% \DeclareMathSizes{12}{20}{14}{10}

@@

\begin{center}
    \large\textbf{Training inhibitory connections between local receptive fields in spiking neural networks}\\
\end{center}

\begin{flushleft}
\begin{tabularx}{\textwidth}{m{4.3cm}m{4.3cm}m{4.3cm}}
Daniil Gafni & Dmitry Nekhaev & Vyacheslav Demin \\
\footnotesize{Lomonosov Moscow State University, Moscow, Russia} & \multicolumn{2}{c}{\footnotesize{National Research Center <<Kurchatov Institute>>, Moscow, Russia}} \bigstrut\\
\small{danielgafni16@gmail.com} & \small{nekhaev.d.v@yandex.ru} & \small{demin.vyacheslav@mail.ru}
\end{tabularx}
\end{flushleft}

\section*{Acknowledgments}
\small{This work was partially supported by the Russian Science Foundation (project № 20-79-10185) in the studying of inhibitory connections training and by the grant INSERT NAME in the part of comparison of concvoltional and locally connected achitectures.}

\addcontentsline{toc}{section}{Abstract}
\section*{Abstract}
Standard learning methods (based on the error backpropagation) used in artificial neural networks (ANNs) are difficult to apply to spiking neural networks (SNNs) due to discrete and time-distributed nature of the events they generate. Although such projects exist, local learning algorithms, which are more biologically correct, capable of performing unsupervised learning and more energy efficient (if implemented on specialized hardware), are of greater interest.

SNN's local learning rules are significantly understudying in comparison to ANNs, and because of this, SNN-based alrorithms produce lower inference quality metrics. Thus, the study of SNN learning algorithms, like spike-timing-dependent-plasticity (STDP), for use in various SNN architectures is an important problem.

The introduction of inhibitory connections (with negative weights) allows to achieve a better distinction of features learned by the neurons. In this work it is shown that learning competition relationships in a locally connected SNN potentially leads to higher pattern recognition accuracy due to the organization of competition and cooperation between groups of neurons.

\section*{Keywords}
Spiking Neural Networks, Unsupervised Learning, Ingibitory Connections, Neuroscience

\section*{Declarations}

\begin{flushleft}
 \begin{tabularx}{\textwidth}{lm{10cm}}
  \textbf{Funding} & {Insert Grant Name} \\
  \textbf{Data, Materials, Code} & {\href{https://github.com/danielgafni/bachelor}{https://github.com/danielgafni/bachelor}} \\
 \end{tabularx}
\end{flushleft}

@@
